\section{Large worlds of mathematical structures}
\subsection{Monoids and Homomorphisms}
Suppose some function $f: \mathbb{N} \rightarrow \mathbb{Z}$ and $f(n)=n$. This function
$f$ respects addition in the following sense.
\begin{align*}
    f(m+n) = f(m) + f(n)
\end{align*}
We can add $m+n$ first and then map it via $f$, or we can first map $m, n$ via
$f$, and then add them.

\begin{ttta}
Another possible function $f: \mathbb{N} \rightarrow \mathbb{Z}$ is given by
$f(n) = 2n$. See if you can check that this also satisfies the above condition
$f(m+n) = f(m) + f(n)$.
\begin{align*}
    f(m+n) =& f(m) + f(n)\\
    2(m+n) =& 2(m) + 2(n)\\
    2(m+n) =& 2(m+n)\\
    m+n =& m+n
\end{align*}
Thus we have shown that $f$ respects addition.
\end{ttta}

\begin{ttta}
Show that this function
\[
f=\set{(0, 0), (1, 1), (2, -1), (3, 2), (4, -2), (5, 3), (6, -3), \dots}
\]
does not respect addition.
\begin{align*}
    f(1+3) =& f(1) + f(3)\\
    f(4) =& f(1) + f(3)\\
    -2 =& 1 + 2\\
    -2 \neq& 3
\end{align*}
\end{ttta}

\begin{ttta}
Mapping into the integers is special because it turns out that respecting
addition forces a function to respect the identity. Prove it.
\end{ttta}
\begin{proofitem}
\item To respect addition a function $f$ must satisfy the following equation $f(m+n) =
f(m)+f(n)$.  Let us suppose that $f$ does respect addition and show that it
implies that $f$ also respects the identity.
\begin{align*}
    f(0+n) =& f(0) + f(n)\\
    f(n) =& f(0) + f(n)\\
    f(0) =& 0
\end{align*}
\end{proofitem}
\begin{definition}
Let $A$ and $B$ be monoids, and write the identity as $1$ and the
binary operation as $\circ$ in each case. Then a monoid homomorphism from A to
B is a function $f:A\rightarrow B$ on the underlying sets, such that
\begin{align*}
    \forall x, y \in A, f(x \circ y) &= f(x) \circ f(y)&&f\text{ respects }\circ\\
    f(1)&=1&&f\text{ respects identity}
\end{align*}
\end{definition}

\begin{ttta}
What do we need to check to show that monoids and their homomorphisms form a
category?
\end{ttta}
\begin{proofitem}
\item Let $M$ be the set of monoids, $M_A, M_B, M_C, \ldots, \in M$.
\item Let $\mathcal{C}_\text{mon}$ be a category where each object is a monoid
    $A\in M$, and each arrow $\times$ is a mapping $A,B \in M, \times:
    A\rightarrow B$.
\item Let $f, g$ be composable functions, ie they are arrows between objects.
\item Let $\circ$ be a binary composition operation on arrows.
\item Let $\ast$ be a binary composition operation on monoidal elements.
\item To show that monoids and their homomorphisms form a cateogry we must show
    the properties of unitality and associativity.
\setcounter{equation}{0}
\begin{align}
    (g\circ f)(x\ast y) &= g(f(x\ast y)) && \text{def. of }\circ\\
    &= g(f(x) \ast f(y)) && f\text{ respects }\ast\\
    &= g(f(x)) \ast g(f(y)) && g\text{ respects }\ast\\
    &= (g\circ f)(x) \ast (g\circ f)(y) && \text{def. of }\circ\\
    (g\circ f)(1)&= g(f(1)) && \text{def. of }\circ\\
    &= g(1) && f \text{ respects }1\\
    &= 1 && g \text{ respects }1
\end{align}
\end{proofitem}
\input{monoid}
\begin{ttta}
Define group homomorphism as a function respecting the group structure. When
dealing with groups, it is redundant to ask for the identity to be preserved.
It’s also redundant to ask for the inverses to be preserved. Prove this.
\end{ttta}
\begin{proofitem}
\item The properties needed for a group are identity, inverse, and
    associativity. We can show that if there exists a function $f$ which is a
    group homomorphism, then we get inverse and identity for freebeez.
\item Suppose $f: G \rightarrow H$ is a homomorphism between groups $G$ and $H$. Then:
\begin{align*}
    f(x\ast x^{-1}) &= f(1_G)\\
    f(x)\ast f(x^{-1}) &= 1_H
\end{align*}
\item Therefore $f(x^{-1})$ is indeed the inverse of $f(x)$ and inverse is
    preserved.
\begin{align*}
    f(x\ast 1_G) &= f(x)\\
    f(x)\ast f(1_G) &= f(x)\\
    f(x^{-1})\ast f(x)\ast 1_H &= f(x^{-1})\ast f(x)\\
    1_H &= f(x\ast x^{-1})\\
    1_H &= f(1_G)
\end{align*}
\item Therefore identity is preserved.
\end{proofitem}
